An IFS study of Low-powered Radio Galaxies

### 2019-09-24 paper.tex
Format changed or something...

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the best-fitting {\bf (Spatially-collapsed? Clarify.)}
stellar spectrum. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA.

>>>>

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the \colorbox{red}{best-fitting {\bf (Spatially-collapsed? 
Clarify.)} stellar spectrum} \colorbox{green}{fits to the stellar 
spectrum for all bins}. For this reason, when fitting the stellar spectra
only \colorbox{red}{{\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}} \colorbox{green}{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA. \colorbox{green}{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}

% Bit more detail needed above****************************************************************************************************************************************************************
